QPLIB: A Library of Quadratic Programming Instances

### 2016-12-27 QPLIB-3.tex
Update QPLIB-3.tex

Figure~\ref{fig:pic_var_small}, Figure~\ref{fig:pic_var_medium} and
Figure~\ref{fig:pic_var_large} describe how discrete and continuous
variables are distributed within the instances. The instances are
sorted accordingly to the total number of variables and, for reason of
readability, the graph is splitted in the three figures:
Figure~\ref{fig:pic_var_small} describes the 100 smaller instances,
Figure~\ref{fig:pic_var_medium} the 200 medium ones, and
Figure~\ref{fig:pic_var_large} the 67 largest ones. For each instance
we report the total number of variables with a ``$+$'', and the total
number of discrete variables (binary or general integer) with a
``$\times$''. The pictures clearly show that instances with different
percentages of integer and continuous variables are present in the
library, and well distributed across the whole spectrum of variable
sizes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_var_small.png}
  \caption{Number of variables (a) \label{fig:pic_var_small}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_var_medium.png}
  \caption{Number of variables (b) \label{fig:pic_var_medium}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_var_big.png}
  \caption{Number of variables (c) \label{fig:pic_var_large}}
\end{figure}

Similarly, Figures~\ref{fig:pic_constr_small}, Figure~\ref{fig:pic_constr_medium}
and Figure~\ref{fig:pic_constr_big} describe how linear and quadratic
constraints are distributed within the instances. The instances are sorted
accordingly to the total number of constraints and divided in the
same manner as for Figures~\ref{fig:pic_var_small}--\ref{fig:pic_var_large}.
For each instances we report the total number of constraints with a ``$+$''
and the total number of (either convex of nonconvex) quadratic constraints
with a ``$\times$''. Also in this case, different percentages of linear and
quadratic constraints are present and well-distributed across the spectrum
of constraint sizes, although both medium- and large-size instances show a
prevalence of lower percentages of quadratic constraints. In particular,
from Figure~\ref{fig:pic_constr_big} we learn that while the maximum number
of linear constraints exceeds 100000, the maximum number of quadratic
constraints tops up at around 10000. This is, however, reasonable, considering
how quadratic constraints can, in general, be expected to be much more
computationally challenging than linear ones, especially if nonconvex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_constr_small.png}
  \caption{Number of constraints (a) \label{fig:pic_constr_small}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_constr_medium.png}
  \caption{Number of constraints (b) \label{fig:pic_constr_medium}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_constr_big.png}
  \caption{Number of constraints (c) \label{fig:pic_constr_big}}
\end{figure}

@@

{\bf Nothing about convexity of constraints? A graph plotting the
number of convex quadratic constraints vs the total number of quadratic
constraints?}

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%  End QPLIB-3.tex
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

>>>>

%Figure~\ref{fig:pic_var_small}, Figure~\ref{fig:pic_var_medium} and
Figure~\ref{fig:pic_var} 
describes how discrete and continuous
variables are distributed within the instances. The instances are
sorted accordingly to the total number of variables.
% and, for reason of
%readability, the graph is splitted in the three figures:
%Figure~\ref{fig:pic_var_small} describes the 100 smaller instances,
%Figure~\ref{fig:pic_var_medium} the 200 medium ones, and
%Figure~\ref{fig:pic_var_large} the 67 largest ones. 
For each instance we report the total number of variables with a ``$+$'', and the total number of discrete variables (binary or general integer) with a ``$\times$''. The pictures clearly show that instances with different percentages of integer and continuous variables are present in the library, and well distributed across the whole spectrum of variable sizes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_var.png}
  \caption{Number of variables \label{fig:pic_var}}
\end{figure}

%\begin{figure}\centering
%  \includegraphics[width=0.85\textwidth]{pic_var_small.png}
%  \caption{Number of variables (a) \label{fig:pic_var_small}}
%\end{figure}
%
%\begin{figure}\centering
%  \includegraphics[width=0.85\textwidth]{pic_var_medium.png}
%  \caption{Number of variables (b) \label{fig:pic_var_medium}}
%\end{figure}
%
%\begin{figure}\centering
%  \includegraphics[width=0.85\textwidth]{pic_var_big.png}
%  \caption{Number of variables (c) \label{fig:pic_var_large}}
%\end{figure}

Similarly, Figures~\ref{fig:pic_constr} 
%Figure~\ref{fig:pic_constr_medium}
%and Figure~\ref{fig:pic_constr_big} 
describes how linear and quadratic
constraints are distributed within the instances. The instances are sorted
accordingly to the total number of constraints
% and divided in the same manner as for Figures~\ref{fig:pic_var_small}--\ref{fig:pic_var_large}.
For each instances we report the total number of constraints with a ``$+$''
and the total number of (either convex of nonconvex) quadratic constraints
with a ``$\times$''. Also in this case, different percentages of linear and
quadratic constraints are present and well-distributed across the spectrum
of constraint sizes, although both medium- and large-size instances show a
prevalence of lower percentages of quadratic constraints. In particular,
from Figure~\ref{fig:pic_constr} we learn that while the maximum number
of linear constraints exceeds 100000, the maximum number of quadratic
constraints tops up at around 10000. This is, however, reasonable, considering
how quadratic constraints can, in general, be expected to be much more
computationally challenging than linear ones, especially if nonconvex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_constr.png}
  \caption{Number of constraints \label{fig:pic_constr}}
\end{figure}

%\begin{figure}\centering
%  \includegraphics[width=0.85\textwidth]{pic_constr_small.png}
%  \caption{Number of constraints (a) \label{fig:pic_constr_small}}
%\end{figure}
%
%\begin{figure}\centering
%  \includegraphics[width=0.85\textwidth]{pic_constr_medium.png}
%  \caption{Number of constraints (b) \label{fig:pic_constr_medium}}
%\end{figure}
%
%\begin{figure}\centering
%  \includegraphics[width=0.85\textwidth]{pic_constr_big.png}
%  \caption{Number of constraints (c) \label{fig:pic_constr_big}}
%\end{figure}

Figure~\ref{fig:pic_conv_constr} shows the instances with at least a quadratic constraints sorted according to the number of quadratic constraints (vertical axis). For each instances we report the total number of constraints with a ``$+$''
and the total number of nonconvex quadratic constraints
with a ``$\times$''.

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{pic_quad_conv_vs_nonconv.png}
  \caption{Quadratic constraints \label{fig:pic_conv_constr}}
\end{figure}

@@

Additional details on the instance features can be found in the Appendix~\ref{sec:instance_details}.
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%  End QPLIB-3.tex
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
